Quotients of the magmatic operad:\\ lattice structures and convergent rewrite systems

### 2018-09-05 Magmatic_operads.tex
MAJ

The union of generating sets of the two operadic ideals $I_1$ and $I_2$
is a generating set of $I_1+I_2$, so that the union of generating
relations for the two operads $\Oca_1$ and $\Oca_2$ of $\QMag$ forms a
generating set for the relations of $\Oca_1\InfQMag\Oca_2$. However, we
do not know how to perform the same method for computing generating
relations for $\Oca_1\SupQMag\Oca_2$ since we do not know how to compute
generating sets of the intersection of two operadic ideals.
\medbreak
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Hilbert series and linear magmatic quotients}
In order to show a Grassmann formula analog for $\LatQMag$, we need the
following lemma.
\medbreak

>>>>

The union of generating sets of the two operadic ideals $I_1$ and $I_2$
is a generating set of $I_1+I_2$, so that the union of generating
relations for the two operads $\Oca_1$ and $\Oca_2$ of $\QMag$ forms a
generating set for the relations of $\Oca_1\InfQMag\Oca_2$. However, the
authors do not know how to compute a generating set of the intersection
of ideals (it is not the intersection of generating relations), so that
we do not know how to compute generating relations for
$\Oca_1\SupQMag\Oca_2$.
\medbreak
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Hilbert series and linear magmatic quotients}
In order to show a Grassmann formula analog for $\LatQMag$, we need the
following lemma.
\medbreak
